---
title: "variablity on R of Cliques"
author: "Fabio Morea"
date: "2023-065-23"
 
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE)
```

```{r load libraries, include=FALSE}
library(igraph)
library(tidyverse)
library(gridExtra)
library(aricode) # NMI 
source('./functions_graph_analysis.R')
```

this is our benchmakrk network

```{r}
getwd()
g<-read_graph('./benchmark/ring_of_cliques/ring_of_cliques_4_6_C_B.gml', format = 'gml')
V(g)$name = seq(1,vcount(g))
shuffled_ids <- sample(vcount(g))
g <- permute.vertices(g, shuffled_ids)

 

layout = layout_with_kk(g)
plot(g, layout = layout)
```

**Some nodes are relevant because they are connected to many other
nodes. For example a person that is in contact with everyone else, a
central node or a pivot node. It has high centrality, high coreness,
high degree. and possibily LOW GAMMA, it is uncertain to attach it to a
specific community**

compare it with "betweenness centrality" (not with "closeness centrality")
High betwenness centrality is correlated with low gamma?
high betwenness centrality means that the node is important in connecting other nodes in the network
if the "Pivot" node was missing, then the distance between other nodes would suddenl icrease.

there
 


```{r}
membership_matrix <- find_communities_N_times (g,
                          n_trials=30,
                          methods=c('IM','ML','LP','FG','LV' ,'WT'),
                          filename_summary = 'ROC_n_trials_summary_results.csv',
                          filename_membership = 'ROC_n_trials_membership.csv')
```

 

########## neighborhood of a graph

```{r}


find_neighbours <- function(g, node_name, order) {
  selected_node_id <- which(V(g)$name == selected_node_name)
  list_neis <- ego(g, order = order, selected_node_id)
  nei_ids <- c()
  for (nn in list_neis) {
    for (x in nn) {
      nei_ids <- append(nei_ids, x)
    }
  }
  nei_ids <- c(nei_ids, selected_node_id)
  nei_ids <- unique(nei_ids)
  return(nei_ids)
}


```


```{r}

g<-read_graph('./benchmark/ring_of_cliques/ring_of_cliques_4_6_C_B.gml', format = 'gml')
V(g)$name <- V(g)$id
selected_node_name <- 3
gg<-induced.subgraph(g, find_neighbours(g, node <- selected_node_name, order = 2))
plot(gg, vertex.color = as.factor(V(gg)$community))
```





```{r}
selected_node_name <- 27
gg<-induced.subgraph(g, find_neighbours(g, node <- selected_node_name, order = 2))
plot(gg, vertex.color = as.factor(V(gg)$community))
```
 


# How to deal with outliers:

## 1 first approach outliers are aggregated to a community
we just set gamma_lim near zero


 
```{r}
method<-'ML'
membership_matrix <- find_communities_N_times (g,
                          n_trials=100,
                          methods=c(method), 
                          filename_summary = '',
                          filename_membership = '')

cons_communities <- consensus(membership_matrix, gamma_lim = 0.2)
V(g)$community<- as.factor(cons_communities$membership)
V(g)$gamma <-  cons_communities$gamma

results <- analyse_communities(g, cons_communities, verbose = TRUE)

cols1 <- c("yellow", "orange", "lightblue", "green", "white")[as.factor(membership(cons_communities))]

plot(cons_communities,g, layout = layout, 
     vertex.label = NA ,  
     col =cols1,
     mark.border =adjustcolor("black", .8), 
     mark.col    =adjustcolor("lightgray", .2))

p1_comms<-cons_communities
p1_g<-g


plot(g, vertex.color = (cons_communities$gamma), 
     vertex.label = if_else(cons_communities$gamma<1,as.character(cons_communities$gamma),''))
plot(g, 
     vertex.size = 30,
     vertex.color = cons_communities$membership, 
     vertex.label = round(cons_communities$gamma,1))

table(cons_communities$membership)

hist(cons_communities$gamma)
table(cons_communities$gamma)
```
```{r}
gc <- make_community_network(g)
gc<-igraph::simplify(gc)
cols4 <- c("yellow", "orange", "lightblue", "green", "white")[as.factor(V(gc)$name)]
plot(gc, 
    vertex.size = V(gc)$size*4, 
    vertex.shape = "square", 
    vertex.color = cols4,
    vertex.label = NA,#V(gc)$size, 
    vertex.label.dist=0.0,
    vertex.label.color='black',
    edge.color = if_else(which_loop(gc), "lightgray", "black"),
    edge.width = E(gc)$weight
    )

p4_gc <- gc


```

## 2 secondo approach: outliers are highlighted as single-node communities
we set gamma_lim above 0.5, as high as 0.0 or 1.0: 
in this case single-node communities are assigned

```{r}

method<-'ML'

membership_matrix <- find_communities_N_times (g,
                          n_trials=100,
                          methods=c(method), 
                          filename_summary = '',
                          filename_membership = '')

 
cons_communities <- consensus(membership_matrix, gamma_lim = 0.9)
V(g)$community<- cons_communities$membership

results <- analyse_communities(g, cons_communities, verbose = TRUE)

cols2 <- c("yellow", "orange", "brown", "lightblue",  "gray", "green",   "darkorchid2", "pink", "lightblue")[as.factor(membership(cons_communities))]

plot(cons_communities,g, layout = layout, 
     vertex.label = NA ,  
     col =cols2,
     mark.border =adjustcolor("black", .8), 
     mark.col    =adjustcolor("lightgray", .2))

p2_comms<-cons_communities
p2_g<-g

plot(g, vertex.color = (cons_communities$gamma), 
     vertex.label = if_else(cons_communities$gamma<1,as.character(cons_communities$gamma),' '))
plot(g, 
     vertex.size = 30,
     vertex.color = cons_communities$membership, 
     vertex.label = round(cons_communities$gamma,1))

table(cons_communities$membership)

hist(cons_communities$gamma)
table(cons_communities$gamma)
```
```{r}
gc <- make_community_network(g)
gc<-igraph::simplify(gc)
cols5 <- c("yellow", "orange", "brown", "lightblue",  "gray", "green",   "darkorchid2", "pink", "blue")

plot(gc, 
    vertex.size = V(gc)$size*10, 
    vertex.shape = "square", 
    vertex.color = cols5,
    vertex.label = NA,#V(gc)$size, 
    vertex.label.dist=0.0,
    vertex.label.color='black',
    edge.color = if_else(which_loop(gc), "lightgray", "black"),
    edge.width = E(gc)$weight
    )
 
p5_gc <- gc

```
 
## 3 third case: outliers are de-focused. we set a higm gamma_lim AND aggregate community labels below gamma_lim to "community zero"
 
```{r}
 
method<-'ML'

membership_matrix <- find_communities_N_times (g,
                          n_trials=100,
                          methods=c(method), 
                          filename_summary = '',
                          filename_membership = '')

 
cons_communities <- consensus(membership_matrix, gamma_lim = 0.9)

#make community zero #############################################
cons_communities$membership [cons_communities$gamma < 0.9] <- 0
V(g)$community <- cons_communities$membership
###################################################################

cons_communities$membership <- as.numeric(cons_communities$membership)
results <- analyse_communities(g, cons_communities, verbose = TRUE)

cols3 <- c("white", "yellow", "orange", "lightblue", "green")[as.factor(membership(cons_communities))]


plot(cons_communities,g, layout = layout, 
     vertex.label = NA ,  
     col =cols3,
     mark.border = if_else(c(T,F,F,F,F) , adjustcolor("white", 0.0), adjustcolor("black", .8)), 
     mark.col    = if_else(c(T,F,F,F,F) , adjustcolor("white", 0.0), adjustcolor("lightgray", .2)))

p3_comms<-cons_communities
p3_g<-g

plot(g, vertex.color = (cons_communities$gamma), 
     vertex.label = if_else(cons_communities$gamma<1,as.character(cons_communities$gamma),''))

plot(g, 
     vertex.size = 30,
     vertex.color = cons_communities$membership, 
     vertex.label = round(cons_communities$gamma,1))

table(cons_communities$membership)

hist(cons_communities$gamma)
table(cons_communities$gamma)
```

 
 # analyse the same results as a network of communities
```{r}

gc <- make_community_network(g)
gc<-igraph::simplify(gc)
col6<-c("white", "yellow", "orange", "lightblue", "green")
plot(gc, 
    vertex.size = V(gc)$size*10, 
    vertex.shape = "square", 
    vertex.color = col6,
    vertex.label = NA, 
    vertex.label.dist=0.0,
    vertex.label.color='black',
    edge.color = if_else(which_loop(gc), "lightgray", "black"),
    edge.width = E(gc)$weight
    )

p6_gc<-gc
 
```
 

 
 
 
 
 
 
 
 
 
 
 
 
 
 
 in una network casuale trovo delle comunità
 con il consensus vedo che 
 1) sono singleton
 2) gamma è molto basso
 
 il mixing factor globale è alto ma insensato: i singleton non vanno interpretati così
 
 
 
```{r}
g<-as.undirected(read.graph('benchmark/random/random_100_0.5.gml', format='gml'))
V(g)$name<-V(g)$id
V(g)$w<-1
V(g)$community<-1
 

method<-'ML'

mp_comms <- find_communities(g, method = method)

membership_matrix <- find_communities_N_times (g,
                          n_trials=50,
                          methods=c(method),#''IM', ML','LP','FG','LV' ,'WT'),
                          filename_summary = 'ROC_n_trials_summary_results.csv',
                          filename_membership = 'ROC_n_trials_membership.csv')

 
cons_results <- consensus(membership_matrix, gamma_lim = 0.5)
V(g)$community<-cons_results$membership
V(g)$gamma<-cons_results$gamma


    gdf<-as_long_data_frame(g) 
    gdf$inter_comm <- (gdf$from_community != gdf$to_community)
    inter_community_links <- sum(gdf$w[ gdf$inter_comm == TRUE]) 
    mu = sum(inter_community_links) / sum(gdf$w)
 print(mu)
 
#make a community object
cons_communities <- make_clusters(g, array(as.numeric(cons_results$membership)))
cons_communities$algorithm <- paste0(method,"_cons")
cons_communities$gamma<-cons_results$gamma
results <- analyse_communities(g, cons_communities, verbose = TRUE)
plot(cons_communities,g, vertex.label = NA)

plot(g, vertex.color = (cons_communities$gamma), 
     vertex.label = if_else(cons_communities$gamma<1,as.character(cons_communities$gamma),''))
plot(g, vertex.color = cons_communities$membership, vertex.label = cons_communities$membership)

#table(cons_communities$membership)
#hist(cons_communities$gamma)
 #table(cons_communities$gamma)
```

 ```{r}
gc <- make_community_network(g, plot = TRUE)

plot(gc, 
    vertex.size = comms$size*4, 
    vertex.shape = "square", 
    vertex.color = V(gc)$name,
    vertex.label = comms$size, 
    vertex.label.dist=0.0,
    vertex.label.color='black',
    edge.color = if_else(which_loop(gc), "lightgray", "black"),
    edge.width = E(gc)$weight/2
    )
 
```


 
 
 
```{r}
g<-as.undirected(read.graph('benchmark/LFR/LFR_benchmark_20.gml', format='gml'))
V(g)$name<-V(g)$id
E(g)$w<-1
#V(g)$community

method<-'ML'

mp_comms <- find_communities(g, method = method)

membership_matrix <- find_communities_N_times (g,
                          n_trials=10,
                          methods=c(method),#''IM', ML','LP','FG','LV' ,'WT'),
                          filename_summary = 'ROC_n_trials_summary_results.csv',
                          filename_membership = 'ROC_n_trials_membership.csv')

 
cons_communities <- consensus(membership_matrix, gamma_lim = 0.9)

#make community zero #############################################
cons_communities$membership [cons_communities$gamma <= 0.9] <- 0
V(g)$community <- cons_communities$membership
V(g)$gamma <- cons_communities$gamma
###################################################################

cons_communities$membership <- as.numeric(cons_communities$membership)
results <- analyse_communities(g, cons_communities, verbose = TRUE)
plot(cons_communities,g, vertex.label = NA)

plot(g, vertex.color = (cons_communities$gamma), 
     vertex.label = if_else(cons_communities$gamma<1,as.character(cons_communities$gamma),''))

plot(g, 
     vertex.size = 30,
     vertex.color = cons_communities$membership, 
     vertex.label = round(cons_communities$gamma,1))

table(cons_communities$membership)

hist(cons_communities$gamma)
table(cons_communities$gamma)
```



```{r}
which(V(g)$gamma <0.8)
selected_node_name <- 244
selected_node_id <- which(V(g)$name == selected_node_name)
list_neis<- ego(g, order = 2, selected_node_id)
nei_ids<- c()
for (nn in list_neis){
  for (x in nn){
    nei_ids <- append(nei_ids, x)
  }
}
nei_ids <- c(nei_ids, selected_node_id)
nei_ids <- unique(nei_ids)
gg<-induced.subgraph(g, nei_ids)
plot(gg, vertex.color = V(gg)$community, vertex.label = V(gg)$id)
```



```{r}
gc <- make_community_network(g, plot = TRUE)
giant_component <- which.max(components(gc)$csize) 
gc1 <- induced.subgraph(gc, components(gc)$membership == giant_component)

plot(gc1, layout = layout.graphopt(gc1),
    vertex.size = V(gc)$size/3, 
    vertex.shape = "square", 
    vertex.color = V(gc)$name,
    vertex.label = V(gc)$size, 
    vertex.label.dist=0.0,
    vertex.label.color='black',
    edge.color = if_else(which_loop(gc), "lightgray", "lightgray"),
    edge.width = E(gc)$weight/20
    )


plot(gc1, layout = layout.graphopt(gc1),
    vertex.size = V(gc)$size/3, 
    vertex.shape = "square", 
    vertex.color = V(gc)$name,
    vertex.label = NA,#V(gc)$name, 
    vertex.label.dist=0.0,
    vertex.label.color='black',
    edge.color = if_else(which_loop(gc), "lightgray", "lightgray"),
    edge.width = E(gc)$weight/20
    )
 
```


 


```{r}
selected_node_name <- 1
selected_node_id <- which(V(g)$name == selected_node_name)
list_neis<- ego(g, order = 2, selected_node_id)
nei_ids<- c()
for (nn in list_neis){
  for (x in nn){
    nei_ids <- append(nei_ids, x)
  }
}
nei_ids <- c(nei_ids, selected_node_id)
nei_ids <- unique(nei_ids)
gg<-induced.subgraph(g, nei_ids)
plot(gg, vertex.color = V(g)$community)
```
 


# FINAL PLOTS


```{r}
par(mfrow=c(2,3), mar=rep(1.0,4), oma=c(0,0,4,0))

#1
plot(p1_comms,p1_g, layout = layout, 
     vertex.label = NA ,  
     col =cols1,
     mark.border =adjustcolor("black", .8), 
     mark.col    =adjustcolor("lightgray", .2))
mtext("incorporate", line=0, side=3, outer=FALSE, cex=1)
mtext("network", line=0, side=1, outer=FALSE, cex=0.6)

#2
plot(p2_comms,p2_g, layout = layout, 
     vertex.label = NA ,  
     col =cols2,
     mark.border =adjustcolor("black", .8), 
     mark.col    =adjustcolor("lightgray", .2))
mtext("highlight", line=0, side=3, outer=FALSE, cex=1)
mtext("network", line=0, side=1, outer=FALSE, cex=0.6)


#3
plot(p3_comms,p3_g, layout = layout, 
     vertex.label = NA ,  
     col =cols3,
     mark.border = if_else(c(T,F,F,F,F) , adjustcolor("white", 0.0), adjustcolor("black", .8)), 
     mark.col    = if_else(c(T,F,F,F,F) , adjustcolor("white", 0.0), adjustcolor("lightgray", .2)))
mtext("group", line=0, side=3, outer=FALSE, cex=1)
mtext("network", line=0, side=1, outer=FALSE, cex=0.6)


#4
plot(p4_gc, 
    vertex.size = V(p4_gc)$size*10, 
    vertex.shape = "square", 
    vertex.color = cols4,
    vertex.label = V(p4_gc)$size, 
    vertex.label.dist=0.0,
    vertex.label.color='black',
    edge.color = if_else(which_loop(p4_gc), "lightgray", "black"),
    edge.width = E(p4_gc)$weight
    )
mtext(" ", line=0, side=3, outer=FALSE, cex=1)
mtext("communities", line=0, side=1, outer=FALSE, cex=0.6)


#5
plot(p5_gc, 
    vertex.size = V(p5_gc)$size*10, 
    vertex.shape = "square", 
    vertex.color = cols5,
    vertex.label = V(p5_gc)$size, 
    vertex.label.dist=if_else(V(p5_gc)$size>1,0.0, 2.0),
    vertex.label.color='black',
    edge.color = if_else(which_loop(p5_gc), "lightgray", "black"),
    edge.width = E(p5_gc)$weight*2
    )
mtext(" ", line=0, side=3, outer=FALSE, cex=1)
mtext("communities", line=0, side=1, outer=FALSE, cex=0.6)


#6
plot(p6_gc, 
    vertex.size = V(p6_gc)$size*10, 
    vertex.shape = "square", 
    vertex.color = col6,
    vertex.label = V(p6_gc)$size, 
    vertex.label.dist=0.0,
    vertex.label.color='black',
    edge.color = if_else(which_loop(p6_gc), "lightgray", "black"),
    edge.width = E(p6_gc)$weight*2
    )
mtext(" ", line=0, side=3, outer=FALSE, cex=1)
mtext("communities", line=0, side=1, outer=FALSE, cex=0.6)


mtext("options for outliers", line=1, side=3, outer=TRUE, cex=1.5)


```
# Florentine
```{r}
library(netrankr)
data("florentine_m")
g<-florentine_m
V(g)$id <- 1:vcount(g)
E(g)$weight <- 1

method <- 'ML'

V(g)$community <- fastgreedy.community(g)$membership
membership_matrix <- find_communities_N_times (g,
                          n_trials=1000,
                          methods=c(method), 
                          filename_summary = '',
                          filename_membership = '')

cons_communities <- consensus(membership_matrix, gamma_lim = 0.2)
V(g)$community<- as.factor(cons_communities$membership)
V(g)$gamma <-  cons_communities$gamma

results <- analyse_communities(g, cons_communities, verbose = TRUE)

cols1 <- c("yellow", "orange", "lightblue", "green", "white")[as.factor(membership(cons_communities))]

plot(cons_communities,g, layout = layout.fruchterman.reingold, 
     vertex.label = NA ,  
     col =cols1,
     mark.border =adjustcolor("black", .8), 
     mark.col    =adjustcolor("lightgray", .2))

 
plot(g, vertex.color = (cons_communities$gamma), 
     vertex.label = if_else(cons_communities$gamma<1,as.character(cons_communities$gamma),''))
plot(g, 
     vertex.size = 30,
     vertex.color = cons_communities$membership, 
     vertex.label = round(cons_communities$gamma,1))

table(cons_communities$membership)

hist(cons_communities$gamma)
table(cons_communities$gamma)

```

