---
title: "CCD on karate-club network"
author: "Fabio Morea"
date: "2023-11-23"
 
output:
  pdf_document: default
---

########################## 

# rif

<https://studentwork.prattsi.org/infovis/labs/zacharys-karate-club/>
immagine ben fatta, con layout ampio

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE)
```

```{r load libraries, include=FALSE}
library(igraph)
library(tidyverse)
library(gridExtra)
library(ggpubr)
library(aricode) # NMI 
library(CCD)
#source('./functions_graph_analysis.R')
```

```{r}
library(igraphdata)
data(karate)
gk <- karate
plot(gk, vertex.label = V(gk)$name)
```

 shapes <- setdiff(shapes(), "")


plot(gk,  layout = layout.graphopt,
     vertex.size = 20,
     vertex.shape = if_else ( comms$membership == 1, "circle", "square"),
     vertex.color = if_else ( comms$gamma == 0, "white", "red"))

 
 ``{r}

#exploring impact of different values of resolution
for (res in seq(.2, 1.6 , 0.2)){
   comms_CCD1 <- CCD::consensus_community_detection(
       gk,
       t = 100,
       p = 0.5,
       method = 'LV',
       resolution = res
   )
   print(paste(res, length(table(comms_CCD1$membership))))
}
 ``

 ``{r}

# given a single resolution, exploring stability for t = 100
comms_CCD1 <- consensus_community_detection(
       gk,
       t = 100,
       p = 0.8,
       method = 'LD',
       resolution = c(0.6 )
   )

for (i in 1:3) {
   comms_CCD2 <-CCD::consensus_community_detection(
           gk,
           t = 100,
           p = 0.8,
           method = 'LD',
           resolution = 0.6 )
    nmi <- aricode::NMI(as.factor(comms_CCD1$membership),as.factor(comms_CCD2$membership))
}

# given t = 100, resolution = 0.5, p = 0.6
# explore gammas
# 
# 
 ``
 
 
```{r}

plot_uncertainty <- function(g,roundgamma = 1) {
  
  df <- data.frame(name = as.factor(V(g)$name),
                   uncertainty =  V(g)$gamma ,
                   community = as.factor( V(g)$community) ,
                   centrality = coreness(g))  
  df <- df[order(df$community, df$name), ]
  df$name <- reorder(  df$name, df$uncertainty )
   
  barchart<-df %>% ggplot()+geom_col(aes(y= name, x = uncertainty, fill = community)) 
  plot(barchart)
  
  layout_fixed <- layout_nicely(g)
  library(RColorBrewer)
  pal <- brewer.pal(length(unique(V(g)$gamma)), "Oranges")
  
  plot(comms_CCD,
      g, layout = layout_fixed,
      #vertex.color = pal[as.numeric(as.factor(V(g)$gamma ))],
      vertex.label = NA,
      #vertex.shape = if_else ( V(k)$community == 1, "circle", "square", "rectangle"),
      vertex.size = coreness(g)*8
  )
  
  gamma_rounded <- round(V(g)$gamma,roundgamma)
  colors_gamma <- pal[as.numeric(as.factor(gamma_rounded ))]
  plot(g,  layout = layout_fixed,
       vertex.label =  gamma_rounded ,
       vertex.size = coreness(g)*8, 
       vertex.color = colors_gamma  )
  legend("topleft", 
         legend = levels(as.factor(gamma_rounded )), 
         col = pal[1:length(levels(as.factor(gamma_rounded )))] , 
         pch = 16, 
         bty = "n")
  
  
   shapes <- setdiff(shapes(), "")
  
  df %>% ggplot(aes(x=centrality, y = uncertainty, color = community)) + 
      geom_point(size = degree(g), alpha = 0.5)+
      theme_light()

}
 
```



```{r}
cons_comms_test <- function(D, p, group_outliers = FALSE, verbose = FALSE, save_results = FALSE){
   
   # definition of community: block within D in which dij > p 
   # this definition includes single node communities (outliers)
   
   # definition of uncertainty coefficient gamma: 
   #     (1-MEAN of di) over all nodes that are at least once in the same community


    
    results <- data.frame(name = colnames(D))
    results$done <- FALSE
    results$tmp_comm_label <- NA
    results$gamma <- NA
    results$comm_size <- NA
    results$single
    community_label <- 0
    nodes_to_process = nrow(results)
     
    while (nodes_to_process > 0)  {
      community_label <-community_label + 1                 
      #select a block with respect to threshold p, first row not done
      nodes_internal <- (D[which.max(results$done == FALSE), ] > p) 
      
      # calculate gamma for eachnode in the block 
      gammas <- D[nodes_internal,  ]
      # ignore nodes that are never in the same community
      gammas[gammas == 0]<-NA
      
      if(sum(nodes_internal)> 1){     # a proper block
        results$gamma[nodes_internal] <-  1- apply(gammas, 1, mean, na.rm=T)
      } else { # a single node
        results$gamma[nodes_internal] <-  1- mean(gammas,  na.rm=T)
      }
      
      results$tmp_comm_label[nodes_internal] <- community_label
      results$comm_size[nodes_internal] <- sum(nodes_internal)
      results$done[nodes_internal] <-  TRUE
      nodes_to_process <- sum(results$done == FALSE)

    } 
    
    results$gamma[ is.na(results$gamma)]<- 0.0
    results$single[  results$comm_size == 1] <- TRUE
    
    if (group_outliers){
      results$tmp_comm_label[ results$single ] <- 0
    }
    
    x <- results %>%
      group_by(tmp_comm_label)%>%
      summarize( n = n()) %>% arrange(-n) %>%
      mutate(cons_comm_label = row_number())
    
    results <- results %>% 
      inner_join (x) %>% 
      select(name,cons_comm_label,gamma,comm_size,single)
    

    if (save_results){ results %>% write_csv('results.csv')}
     
    return(results)
}  

```

```{r}

t = 301
p = 0.8
method = 'LV'

shuffle = TRUE

g<-gk
 
 M <- CCD::find_communities_repeated(
            g,
            n_trials = t,
            method = method,
            shuffle = shuffle,
            resolution = c(0.7),  #for Louvain or Leiden
            steps = 4,            #for walwtrap
            verbose = F
        )
 
nco <- CCD::normalized_co_occurrence(M)

CC <- cons_comms_test(nco, p = p, verbose = T, save_results = T)
        
comms_CCD <- make_clusters(g, array(as.numeric(CC$cons_comm_label)))
comms_CCD$gamma <- CC$gamma
comms_CCD$name <- CC$name
        

V(g)$community <- comms_CCD$membership[ order(match(comms_CCD$name, V(g)$name)) ]
V(g)$gamma <- round( comms_CCD$gamma,4)

plot(comms_CCD, g)
print(paste("Number of communities", max(V(g)$community)))


table(V(g)$gamma)
hist(V(g)$gamma)


 plot_uncertainty(g, roundgamma=2)

```

# test on a Ring of Cliques with 3 single node components
```{r}
rc <-CCD::make_ring_of_cliques(num_cliques = 4, clique_size = 5, add_bridges = T, add_center = T)
rc <- rc %>% add_vertices(3)  
V(rc)$name <- seq(1:vcount(rc))
plot(rc)
 
t =  501

p = 0.7
method = 'WT'

shuffle = T

g<-rc
 
 M <- CCD::find_communities_repeated(
            g,
            n_trials = t,
            method = method,
            shuffle = shuffle,
            resolution = c( 1.0),  #for Louvain or Leiden
            steps = 4,            #for walwtrap
            verbose = F
        )
 
nco <- CCD::normalized_co_occurrence(M)

CC <- cons_comms_test(nco, p = p, 
                      group_outliers = F, 
                      verbose = T,
                      save_results = T)
        
comms_CCD <- make_clusters(g, array(as.numeric(CC$cons_comm_label)))
comms_CCD$gamma <- CC$gamma
comms_CCD$name <- CC$name
        

V(g)$community <- comms_CCD$membership[ order(match(comms_CCD$name, V(g)$name)) ]
V(g)$gamma <- round( comms_CCD$gamma,6)

plot(comms_CCD, g)
print(paste("Number of communities", max(V(g)$community)))


table(V(g)$gamma)
hist(V(g)$gamma)

  plot_uncertainty(g, roundgamma=1)

```
`
