---
title: "CCD on karate-club network"
author: "Fabio Morea"
date: "2023-11-23"
 
output:
  pdf_document: default
---

########################## 

# rif

<https://studentwork.prattsi.org/infovis/labs/zacharys-karate-club/>
immagine ben fatta, con layout ampio

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE)
library(devtools)  

devtools::install_github("fabio-morea/CCD", force = TRUE)
library(CCD)

library(igraph)
library(tidyverse)
 
library(gridExtra)
library(ggpubr)
library(aricode) # NMI 
library(plotly)  
library(scales)
library(RColorBrewer)
```

```{r}
library(igraphdata)
data(karate)
gk <- karate
plot(gk, vertex.label = V(gk)$name)
```

 shapes <- setdiff(shapes(), "")


plot(gk,  layout = layout.graphopt,
     vertex.size = 20,
     vertex.shape = if_else ( comms$membership == 1, "circle", "square"),
     vertex.color = if_else ( comms$gamma == 0, "white", "red"))

 
 ``{r}

#exploring impact of different values of resolution
for (res in seq(.2, 1.6 , 0.2)){
   comms_CCD1 <- CCD::consensus_community_detection(
       gk,
       t = 100,
       p = 0.5,
       method = 'LV',
       resolution = res
   )
   print(paste(res, length(table(comms_CCD1$membership))))
}
 ``

 ``{r}

# given a single resolution, exploring stability for t = 100
comms_CCD1 <- consensus_community_detection(
       gk,
       t = 100,
       p = 0.8,
       method = 'LD',
       resolution = c(0.6 )
   )

for (i in 1:3) {
   comms_CCD2 <-CCD::consensus_community_detection(
           gk,
           t = 100,
           p = 0.8,
           method = 'LD',
           resolution = 0.6 )
    nmi <- aricode::NMI(as.factor(comms_CCD1$membership),as.factor(comms_CCD2$membership))
}

# given t = 100, resolution = 0.5, p = 0.6
# explore gammas
# 
# 
 ``
 
 
```{r}

plot_uncertainty <- function(g,comms, roundgamma = 1) {
  
  df <- data.frame(name = as.factor(V(g)$name),
                   uncertainty =  round(V(g)$gamma, roundgamma),
                   community = as.factor( V(g)$community) ,
                   centrality = coreness(g))  
  df <- df[order(df$community, df$name), ]
  df$name <- reorder(  df$name, df$uncertainty )
   
  barchart<-df %>% ggplot()+geom_col(aes(y= name, x = uncertainty, fill = community)) 
  print(ggplotly(barchart))
  
  
  layout_fixed <- layout_nicely(g)

  palette_comms <- rev(brewer.pal(length(unique(V(g)$community)), "Greys"))
  for (i in 1:length(palette_comms)){
      palette_comms[i] <- adjustcolor( palette_comms[i] , alpha.f = .6)
  }

  palette_gamma <- brewer.pal(length(unique(V(g)$gamma)), "Oranges")

 
plot(CC,
      g,  
      col = palette_gamma[as.numeric(as.factor(V(g)$gamma))],
      mark.border="black", 
      mark.col= palette_comms,
      vertex.label =  NA ,
      vertex.size = coreness(g)*3
  )
  legend("topleft", 
         title = "uncertainty",
         legend = levels(as.factor(V(g)$gamma  )), 
         col = palette_gamma[1:length(levels(as.factor(V(g)$gamma )))] , 
         pch = 16, 
         bty = "n")
    legend("topright", 
         title = "community",
         legend = rev(unique(V(g)$community)), 
         col = palette_comms[1:length(unique(V(g)$community))] , 
         pch = 16, 
         bty = "n")
  
   
  
  bubblechart <- df %>% ggplot(aes(x=centrality, y = uncertainty, color = community)) + 
      geom_point(size = degree(g), alpha = 0.5)+
      theme_light()  
  print(ggplotly(bubblechart))

}
 
```

 


 
```{r}
g<-gk

CC <-CCD::consensus_community_detection(
        g,
        p = 0.80,
        t = 501,
        group_outliers = FALSE,
        method = 'LV',
        resolution = c(0.7),
        shuffle = TRUE
    )

#V(g)$community <- CC$membership[order(match(CC$name, V(g)$name))]
V(g)$community <- CC$membership 
V(g)$gamma <- round(CC$gamma, 2)
V(g)$comm_size <- CC$comm_size

plot(CC, g)
print(paste("Number of communities", max(V(g)$community)))
table(V(g)$gamma)
hist(V(g)$gamma)


plot_uncertainty(g, CC,roundgamma = 2)


 



```


# test stability  as a function of t and *p*
How many communities are there?
Are 9 and 31 with Han or not?

```{r}
M <- NA
reps <- 100
df <- data.frame()
g<-gk
for (t in c(1, 11, 21, 51, 101 )) {
  print(paste("Testing t = ", t))
  for (j in 1:reps) {
    gs <-igraph::permute(g, sample(1:vcount(g), size = vcount(g), replace = FALSE))
    commsCCD <- CCD::consensus_community_detection(g, method = 'LP', r = c(0.7), t = t)
    V(g)$community <-commsCCD$membership[order(match(commsCCD$name, V(g)$name))]
    uncertain_nodes <- sum(commsCCD$gamma>0)/vcount(g)
    uncertainty_q10 <- round(quantile(commsCCD$gamma[ commsCCD$gamma >0], 0.10),6)
    uncertainty_q50 <- round(quantile(commsCCD$gamma[ commsCCD$gamma >0], 0.50),6)
    uncertainty_q90 <- round(quantile(commsCCD$gamma[ commsCCD$gamma >0], 0.90),6)
    nmi <- aricode::NMI(as.factor(V(g)$community), as.factor(V(g)$Faction))
    nc=max(commsCCD$membership)
    df<-rbind(df,data.frame(t,nmi,nc))
    }
}
df %>% ggplot(aes(x=as.factor(t), y=nmi))+geom_boxplot()+geom_point(alpha=.5)
df %>% ggplot(aes(x=as.factor(t), y=nc))+geom_boxplot()+geom_point(alpha=.5)

 
dfsumm<- df %>% group_by(t) %>% summarize(
    nmi_mean = mean(nmi ),
    lower_quantile = quantile(nmi, 0.05),
    upper_quantile = quantile(nmi, 0.95))

ggplot( ) +
  geom_ribbon(data = dfsumm, 
              aes(x=t, ymin = lower_quantile, ymax = upper_quantile  ), 
              fill = "lightyellow", alpha = .8)  +
  geom_point(data = df, aes(x = t, y = nmi)) + 
  geom_boxplot(data = df, aes(x = t, y = nmi, group = t)) + 
  geom_line(data = dfsumm, aes(x = t, y = nmi_mean))+
  theme_light()


```


# test on a Ring of Cliques with 3 single node components
```{r}
rc <-CCD::make_ring_of_cliques(num_cliques = 6, clique_size = 8, add_bridges = T, add_center = T)
#rc <- rc %>% add_vertices(3)  
#V(rc)$name <- seq(1:vcount(rc))
#plot(rc)
 
g<-rc
CC <-CCD::consensus_community_detection(
        g,
        p = 0.8,
        t = 501,
        group_outliers = T,
        method = 'WT',
        resolution = c(0.7),
        shuffle = T
    )
        


V(g)$community <- CC$membership[ order(match(CC$name, V(g)$name)) ]
V(g)$gamma <- round( CC$gamma,2)

plot(CC, g)
print(paste("Number of communities", max(V(g)$community)))


table(V(g)$gamma)
hist(V(g)$gamma)
plot_uncertainty(g, CC, roundgamma=1)

```
`
