---
title: "variablity and order bias on Ring of Cliques"
author: "Fabio Morea"
date: "2023-06-23"
 
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE)
```


```{r load library, message=FALSE, warning=FALSE}
library(devtools)  
#devtools::install_github("fabio-morea/CCD")
library(CCD)
library(igraph)
library(tidyverse)
```
 


```{r}
#a function to plot the RIng of Cliques

plot_roc <- function( comms, g) {
  
  vertex_colors <- rep( "orange", vcount(g))
  vertex_colors <- if_else (V(g)$gamma < 0.60,  "yellow",vertex_colors)
  vertex_colors <- if_else (V(g)$gamma < 0.1,  "white",vertex_colors)
   
      
  plot(comms,g,  
       vertex.label=V(g)$gamma, 
       vertex.size = 30, 
       edge.width = E(g)$weight)
  
  
  plot(g,  layout = layout_with_kk,
       vertex.color =vertex_colors,
       vertex.label=V(g)$gamma, 
       vertex.size = 30, 
       edge.width = E(g)$weight)
  
  table(V(g)$gamma)
  
  hist(V(g)$gamma)
  
  plot(V(g)$core ,V(g)$gamma)

}
```


Make a RoC. 
```{r}
g<-CCD::make_ring_of_cliques(num_cliques = 4, 
                             clique_size = 5, 
                             add_center = TRUE, 
                             add_bridges = TRUE)

print(g)
print(table(degree(g)))
```
```{r}
plot(g,  vertex.label = V(g)$community,  vertex.color = "white")
substr( V(g)$community , start = 1 , stop = 1 )

 

```

Network are inherently NON-ordered. But their practical implementation in R is inhevitably ordered. 
Specifically this ring of cliquest was built following a the order shown in the figure above. The adjacency matrix clearly shows the communities as blocks.
```{r}
adj_matrix_g <- igraph::as_adjacency_matrix(g)
print(adj_matrix_g)
```

if we permute the nodes, we obtain the following matrix:
```{r}
gs <- igraph::permute(g, 
                              sample(1:vcount(g), 
                              size = vcount(g), 
                              replace = FALSE ) )

adj_matrix_gs <- igraph::as_adjacency_matrix(gs)
print(adj_matrix_gs)
plot(gs, vertex.size = 25)
print(gs)
```

The shuffled version has the same nodes id, but ordered differently. However, we expect to find the same communities in g adn gs.

# selecting the appropriate value of resolution

LD has different bahaviour depending on resolution
resolution near 0 incorporates
resolution below 1.0 highlights
resolution above 1.0 finds individual communities, non valid
Hence we use LD with resolution = 0.15 so it generates aggregations
```{r}
resols = seq(0.05, 1.5, 0.05)
for (resol in resols){
  comms_g <- cluster_leiden(g, resolution = resol)
  print(paste(resol, max(comms_g$membership)))
}
```

Lv is always incorporating, hence resolution = 1.0
```{r}
resols = seq(0.05, 1.5, 0.05)
for (resol in resols){
  comms_g <- cluster_louvain(g, resolution = resol)
  print(paste(resol, max(comms_g$membership)))
}
```

```{r}
# leiden: resolution = 1.0 generates single-node clusters, probably due to the simmetry of this network. We set resolution = 0.99, which generates larger communities. 
# 
comms_g <- cluster_leiden(g, resolution = .15)
comms_gs <- cluster_leiden(gs, resolution = .15)
plot(comms_g,g, main = "Leiden - original network", vertex.label = V(g)$community)
plot(comms_gs,gs, main = "Leiden - shuffled network", vertex.label = V(gs)$community)
```

```{r}
comms_g <- cluster_louvain(g, resolution = 1)
comms_gs <- cluster_louvain(gs, resolution = 1)
plot(comms_g,g, main = "Louvain - original network")
plot(comms_gs,gs, main = "Louvain - shuffled network")
```

We may expect that the central node is assigned randompy to one of the four communities. In fact this happens only in the shuffled network.
```{r}
center_id <- which(V(g)$community=="A")
print(paste("The central node id is ", center_id))
results <- data.frame()
for (i in 1:100) {
        #comms <- cluster_leiden(g, resolution = 0.99)
        comms <- cluster_louvain(g, resolution = 1)
        #comms <- fastgreedy.community(gs)
        nc <- max(comms$membership)
        m_center <- comms$membership[center_id]
        results <- rbind(results, data.frame( nc, m_center))
}
print("Central node is assigned to the following communities")
table(results$m_center)
plot(comms, g)
```

Repeat, shuffling the graph at each trial
```{r}

results_s <- data.frame()
for (i in 1:1000) {
  gs <- igraph::permute(g, 
                              sample(1:vcount(g), 
                              size = vcount(g), 
                              replace = FALSE ) )
  center_id <- which(V(g)$community=="A")
  
  #print(paste("The central node id is ", center_id))
  
comms <- cluster_louvain(gs, resolution = 1)
  #comms <- cluster_leiden(gs, resolution = 0.99)
#comms <- walktrap.community(gs)
#  comms <- label.propagation.community(gs)
#comms <- infomap.community(gs)

  
  nc <- max(comms$membership)
  m_center <- comms$membership[center_id]
  results_s <- rbind(results_s, data.frame( nc, m_center))
}
print("Central node is assigned to the following communities")
table(results_s$m_center)
plot(comms, gs)

```

# analysis of bridge node 24 (connected to 2 and 16)

```{r}
chech_bridge <- function(nb = 24,
                         n_left = 2,
                         n_right = 16,
                         labels) {
  if (labels[n_right] == labels[n_left]) {
    #print(paste("incorporated", labels[nb], labels[n_left], labels[n_right]))
    return("I")
  } else if (labels[n_right] == labels[nb]) {
    #print(paste("bridge", labels[nb], "is incorporated with", labels[n_right]))
    return("R")
  }  else if (labels[n_left] == labels[nb]) {
    #print(paste("bridge", labels[nb], "is incorporated with", labels[n_left]))
    return("L")
  } else {
    #print(paste("bridge", labels[nb], "is a single node community"))
    return("S")
  }
}

results_bridge = c()
for (i in 1:1000){
  comms_g <- cluster_louvain(g, resolution = .99)
  results_bridge <- c(results_bridge, 
                      chech_bridge(nb = 24,
                         n_left = 2,
                         n_right = 16,
                         labels = comms_g$membership))
}
table(results_bridge)

```


```{r}

check_center <- function(own_communities,assigned_communities, selected_com_label, verbose = FALSE) {
  # if the center is a single-node community returns "S"
  # else returns the community label to which the center is assocaited
  #
  center_id <- which(V(g)$community=="A")
  comm_assigned_to_center <- assigned_communities[center_id]
  comm_size_center <- length( assigned_communities [ assigned_communities == comm_assigned_to_center])
  if (comm_size_center == 1){
    return(  "S" )
  } else {
    x <- own_communities[assigned_communities == comm_assigned_to_center]
    if (x[1] !="A"){return(x[1])} else{return(x[2])}
    #y <- x[- which((x) == "A")]
    return()
  }
 
}




results_center = c()
for (i in 1:100){
  comms_g <- cluster_leiden(g, resolution_parameter = .11)
  results_center <- c(results_center, 
                      check_center(own_communities = V(g)$community,
                                   assigned_communities = comms_g$membership,
                                   verbose = TRUE))
}
table(results_center)
plot(comms_g,g) 


```

```{r}

```


# analysis of order bias t = 1000
```{r}

find_communities <- function(g,method,  verbose = FALSE) {
    # applies selected method
    # applies resolution for LV and LD
    # undirected(g) for LV and LD
    # 
    method = substr(method, 1, 2)
    if (method == "LV") {
        comms <- cluster_louvain(as.undirected(g, mode = 'each'), resolution = 1)
    } else if (method == "LD") {
        comms <-
            cluster_leiden(as.undirected(g, mode = 'each'), 
                           #resolution_parameter = quantile(strength(g))[2] / (gorder(g) - 1)
                           resolution_parameter = 0.15
                           )
    } else if (method == "IM") {
        comms <- infomap.community(g)
    } else if (method == "LP") {
        comms <- label.propagation.community(g)
    } else if (method == "WT") {
        comms <- walktrap.community(g)
    } else {
        print("No valid method")
        stop
    }
    comms$algorithm = method
    
    if (verbose == TRUE) {
        print(paste("Community detection with ", method, "completed."))
    }
    return(comms)
}

```

# FIGURE for paper


```{r}
g<-CCD::make_ring_of_cliques(num_cliques = 4, 
                             clique_size = 5, 
                             add_center = TRUE, 
                             add_bridges = FALSE)
comms = 0
trials = 1000
methods <- c( 'IM','LD', 'LP', 'LV', 'WT')
shuff = "G"
results <- data.frame()

for (met in methods) {
    for (i in 1:trials) {
        comms_g <- find_communities(g, met)
        nc <- max(comms_g$membership)
        m_center <- check_center(own_communities = V(g)$community,
                                 assigned_communities = comms_g$membership)
        results <- rbind(results, data.frame(met, shuff, nc, m_center))

    }
}
 
##shuffle ids before comm detection

shuff = "G*"
 
for (met in methods) {
    for (i in 1:trials) {
        gs <- igraph::permute(g, sample(1:vcount(g), size = vcount(g), replace = FALSE ) )
        comms_gs <- find_communities(gs, met)
        nc <- max(comms_gs$membership)
        m_center <- check_center(own_communities = V(gs)$community,
                                 assigned_communities = comms_gs$membership)
     results <- rbind(results, data.frame(met, shuff, nc, m_center))

    }
}



table_center_shuffled <- results %>% filter(shuff == 'G*')%>% 
    mutate(algorithm = met)%>% select(-met)%>%
    group_by(algorithm, m_center) %>%
  summarise(n = n()) %>%
  mutate(freq =  (n / sum(n))) %>%
    select(-n)%>%
    arrange(m_center)%>%
    pivot_wider(names_from = m_center, values_from = freq, values_fill = 0.00) 


table_center_fixed <- results %>% filter(shuff == 'G')%>%
    mutate(algorithm = met)%>% select(-met)%>%
    group_by(algorithm, m_center) %>%
  summarise(n = n()) %>%
  mutate(freq =  (n / sum(n))) %>%
    select(-n)%>%
    arrange(m_center)%>%
    pivot_wider(names_from = m_center, values_from = freq, values_fill = 0.00) 

print(table_center_fixed%>%arrange(algorithm))

print(table_center_shuffled%>%arrange(algorithm))




```

```{r}
results %>%  rename(algorithm = met)%>%
  ggplot(aes(y = m_center, fill = algorithm))+geom_bar()+facet_grid(shuff~ algorithm)+ theme_bw()+
  geom_vline(xintercept = 250, linetype = 'dashed') + theme(aspect.ratio = 1.1) + 
  xlab('number of assignation over 1000 trials')+
  ylab('label assigned to central node')

```


```{r}
g<-CCD::make_ring_of_cliques(num_cliques = 3, 
                             clique_size = 10, 
                             add_center = TRUE, 
                             add_bridges = FALSE)
comms = 0
trials = 1000
methods <- c( 'IM','LD', 'LP', 'LV', 'WT')
shuff = "G"
results <- data.frame()

for (met in methods) {
    for (i in 1:trials) {
        comms_g <- find_communities(g, met)
        nc <- max(comms_g$membership)
        m_center <- check_center(own_communities = V(g)$community,
                                 assigned_communities = comms_g$membership)
        results <- rbind(results, data.frame(met, shuff, nc, m_center))

    }
}
 
##shuffle ids before comm detection

shuff = "G*"
 
for (met in methods) {
    for (i in 1:trials) {
        gs <- igraph::permute(g, sample(1:vcount(g), size = vcount(g), replace = FALSE ) )
        comms_gs <- find_communities(gs, met)
        nc <- max(comms_gs$membership)
        m_center <- check_center(own_communities = V(gs)$community,
                                 assigned_communities = comms_gs$membership)
     results <- rbind(results, data.frame(met, shuff, nc, m_center))

    }
}



table_center_shuffled <- results %>% filter(shuff == 'G*')%>% 
    mutate(algorithm = met)%>% select(-met)%>%
    group_by(algorithm, m_center) %>%
  summarise(n = n()) %>%
  mutate(freq =  (n / sum(n))) %>%
    select(-n)%>%
    arrange(m_center)%>%
    pivot_wider(names_from = m_center, values_from = freq, values_fill = 0.00) 


table_center_fixed <- results %>% filter(shuff == 'G')%>%
    mutate(algorithm = met)%>% select(-met)%>%
    group_by(algorithm, m_center) %>%
  summarise(n = n()) %>%
  mutate(freq =  (n / sum(n))) %>%
    select(-n)%>%
    arrange(m_center)%>%
    pivot_wider(names_from = m_center, values_from = freq, values_fill = 0.00) 

print(table_center_fixed%>%arrange(algorithm))

print(table_center_shuffled%>%arrange(algorithm))

 
results %>%  rename(algorithm = met)%>%
  ggplot(aes(y = m_center, fill = algorithm))+geom_bar()+facet_grid(shuff~ algorithm)+ theme_bw()+
  geom_vline(xintercept = 250, linetype = 'dashed') + theme(aspect.ratio = 1.1) + 
  xlab('number of assignation over 1000 trials')+
  ylab('label assigned to central node')

```
  
  